Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code summary statistics

# Concentration evel
statistics_concentration <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  provide_statistics(Concentration)

>>>>

# Concentration evel
statistics_concentration <- d_transcript %>%
  inner_join(
    d_course,
    by = "Course ID"
    ) %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration)
